\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{setspace}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{array}
\usepackage{longtable}
\geometry{margin=1in}
\setstretch{1.25}
\setlength{\parindent}{2em}
\setlength{\parskip}{0.4em}

\begin{document}

\begin{titlepage}
\vspace*{\fill}
\begin{center}
{\LARGE \textbf{Bachelor Project Plan}\par}
\end{center}
\vspace{2em}
\raggedright
{\large \textbf{Name:} Xuanlin Chen\par}
{\large \textbf{Advisor:} Prof.\ Piotr Didyk\par}
{\large \textbf{Title:} Fluid Simulation and Real-Time Rendering of Shallow Water Equations\par}
\vspace*{\fill}
\end{titlepage}

\section*{Project Objectives}
This project aims to simulate water-surface behavior by numerically solving the shallow water equations (SWE). It focuses on dynamic fluctuations, user interaction, and real-time rendering for large-scale water scenes while preserving physical plausibility.

\section*{Work Plan}
\renewcommand{\arraystretch}{1.2}
\begin{longtable}{>{\centering\arraybackslash}p{1cm} p{4.5cm} p{6cm} p{2.8cm}}
\toprule
\textbf{Week} & \textbf{Planned Activity} & \textbf{Expected Result} & \textbf{Current Status} \\
\midrule
\endfirsthead

\toprule
\textbf{Week} & \textbf{Planned Activity} & \textbf{Expected Result} & \textbf{Current Status} \\
\midrule
\endhead

\midrule
\multicolumn{4}{r}{\small Continued on next page} \\
\endfoot

\bottomrule
\endlastfoot

W1 & Setup environment and basic shaders & The screen can render a static plane with simple colors. & Completed \\
W2 & Implement SWE base update cycle & The fundamental changes in the height field can be observed. & Completed. Add a linear solver in pipelines \\
W3 & Staggered grid \& advection implementation & Stable fluid motion & Completed \\
W4 & CFL condition \& fluctuation handling & Numerically stable simulation & Completed (While stability cannot maintain in wet-dry boundary conditions.) \\
W5 & Blinn-Phong shading implementation & Giving the waveform a sense of depth and light and shadow feedback. & Completed with PBR instead. \\
W6 & Real-time vertex height displacement & Dynamic water mesh & Completed\\
W7 & Implement Boundary conditions & Constrained fluid behavior & Cancelled(now merge with W4) \\
W7 & Impement the clipmap. &To reduce FPS load, so resolutions will change according to the distance to camera. & Completed.(New target) \\
W8 & Environment mapping \& Fresnel effect & Enhanced water aesthetics & Completed(using cubemap for skybox now, may change in May) \\
W9 & Solid-fluid coupling & Interaction with dynamic objects & In progress (now can simply interact with a boat.) \\
W10 & Particle system / Foam map & Visual detail enrichment & Planned in May.\\
W11 & Performance optimization & Real-time frame rate stability & Planned in May. \\
W12 & Final documentation & Completed Thesis Report & Planned.\\
\end{longtable}
\end{document}